Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-05-20 article-models-ttinternal.tex
starting to implement the new code in the text

\begin{defn}
An \emph{extension algebra in context $\Gamma$} is a quadruple $(A,P,\epsilon_0,\epsilon_1)$
consisting of a family $A$ over context $\Gamma$, a family $P$ over the context
$\ctxext{\Gamma}{A}$, a morphism $\epsilon_0$ from $\ctxext{A}{P}$ to $A$ in context
$\Gamma$ and a morphism $\epsilon_1$ from $\ctxext{P}{\jcomp{}{\epsilon_0}{P}}$ to $P$ in context
$\ctxext{\Gamma}{A}$, satisfying the judgmental equalities of
\autoref{eq:extalg-eq1,eq:extalg-eq2}.
\end{defn}

@@

\begin{defn}
Let $\mathcal{A}$ and $\mathcal{B}$ be term-algebras in context $\Gamma$. 
A term-operation from $\mathcal{A}$ to $\mathcal{B}$ is a triple $(f_0,f_1,f_2)$
consisting of
\begin{align*}
\jhom*{\Gamma}{A}{B}{f_0}
  \\
\jfhom*{\Gamma}{A}{B}{f_0}{P}{Q}{f_1}
  \\
\jfhom*{\Gamma}{{A}{P}}{{B}{Q}}{\jvcomp{P}{f_0}{f_1}}{T}{U}{f_2}
\end{align*}
such that the pair $(f_0,f_1)$ is both an extension homomorphism from
$(A,P,\epsilon_0,\epsilon_1)$ to $(B,Q,\eta_0,\eta_1)$ in context $\Gamma$
and an empty homomorphism from $(A,P,\phi_0,\phi_1)$ to $(B,Q,\psi_0,\psi_1)$
in context $\Gamma$.
\end{defn}

>>>>

\begin{defn}
An \emph{extension algebra $\cftalg{A}$ in context $\Gamma$} is a quadruple 
\begin{equation*}
(\cftalgc{\cftalg{A}},\cftalgf{\cftalg{A}},\cftctxext{\cftalg{A}},\cftfamext{\cftalg{A}})
\end{equation*}
consisting of a family $\cftalgc{\cftalg{A}}$ over context $\Gamma$, 
a family $\cftalgf{\cftalg{A}}$ over the context
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$,
a morphism $\cftctxext{\cftalg{A}}$ from $\ctxext{\cftalgc{\cftalg{A}}}{
\cftalgf{\cftalg{A}}}$ to $\cftalgc{\cftalg{A}}$ in context
$\Gamma$ and a morphism $\cftfamext{\cftalg{A}}$ from 
$\ctxext{\cftalgf{\cftalg{A}}}{\jcomp{}{\cftctxext{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}$ 
to $\cftalgf{\cftalg{A}}$ in context
$\ctxext{\Gamma}{\cftalgc{\cftalg{A}}}$, satisfying the judgmental equalities of
\autoref{eq:extalg-eq1,eq:extalg-eq2}.
\end{defn}

@@

\begin{defn}
Let $\cftalg{A}$ and $\cftalg{B}$ be term-algebras in context $\Gamma$. 
A term-operation $\cfthom{f}$ from $\cftalg{A}$ to $\cftalg{B}$ in context
$\Gamma$ is a triple $(\cfthomc{\cfthom{f}},\cfthomf{\cfthom{f}},\cfthomt{\cfthom{f}})$
consisting of
\begin{align*}
\jhom*{\Gamma}{\cftalgc{\cftalg{A}}}{\cftalgc{\cftalg{B}}}{\cfthomc{\cfthom{f}}}
  \\
\jfhom*
  {\Gamma}
  {\cftalgc{\cftalg{A}}}
  {\cftalgc{\cftalg{B}}}
  {\cfthomc{\cfthom{f}}}
  {\cftalgf{\cftalg{A}}}
  {\cftalgf{\cftalg{B}}}
  {\cfthomf{\cfthom{f}}}
  \\
\jfhom*
  {\Gamma}
  {{\cftalgc{\cftalg{A}}}{\cftalgf{\cftalg{A}}}}
  {{\cftalgc{\cftalg{B}}}{\cftalgf{\cftalg{B}}}}
  {\jvcomp{\cftalgf{\cftalg{A}}}{\cfthomc{\cfthom{f}}}{\cfthomf{\cfthom{f}}}}
  {\cftalgt{\cftalg{A}}}
  {\cftalgt{\cftalg{B}}}
  {\cfthomt{\cfthom{f}}}
\end{align*}
such that the pair $(\cfthomc{\cfthom{f}},\cfthomf{\cfthom{f}})$ is both an 
extension homomorphism from
$(\cftalgc{\cftalg{A}},\cftalgf{\cftalg{A}},\cftctxext{\cftalg{A}},\cftfamext{\cftalg{A}})$ 
to 
$(\cftalgc{\cftalg{B}},\cftalgf{\cftalg{B}},\cftctxext{\cftalg{B}},\cftfamext{\cftalg{B}})$ 
in context $\Gamma$
and an empty homomorphism from 
$(\cftalgc{\cftalg{A}},\cftalgf{\cftalg{A}},\cftempc{\cftalg{A}},\cftempf{\cftalg{A}})$
to
$(\cftalgc{\cftalg{B}},\cftalgf{\cftalg{B}},\cftempc{\cftalg{B}},\cftempf{\cftalg{B}})$
in context $\Gamma$.
\end{defn}

Thus, when $\cfthom{f}$ is a term-operation from $\cftalg{A}$ to $\cftalg{B}$, we are
in the situation of the following judgmentally commutative diagram:
\begin{equation*}
\begin{tikzcd}
\cftalgt{\cftalg{A}}
  \ar[fib]{d}
  \ar{r}{\cfthomt{\cfthom{f}}}
& \cftalgt{\cftalg{B}}
  \ar[fib]{d}
  \\
\cftalgf{\cftalg{A}}
  \ar[fib]{d}
  \ar{r}{\cfthomf{\cfthom{f}}}
& \cftalgf{\cftalg{B}}
  \ar[fib]{d}
  \\
\cftalgc{\cftalg{A}}
  \ar{r}{\cfthomc{\cfthom{f}}}
& \cftalgc{\cftalg{B}}
\end{tikzcd}
\end{equation*}
